Analysis for Project

### 2021-11-22 analysis/analysis.Rmd
Better figure to test coding of below expected grade

```{r tab-grade-by-age}
tbl <- table(acs$age, acs$current_grade)

acs %>% 
  tabyl(age, current_grade) %>%
  mutate_if(is.numeric, format, big.mark=",") %>%
  kbl(caption="Cross-tabulation of age and current grade of student",
      align=c("l",rep("r",13))) %>%
  kable_paper() %>%
  column_spec(2, background=c(rep("#D3D3D3",2), rep("white", 14))) %>%
  column_spec(3, background=c("white", 
                              rep("#D3D3D3",2), 
                              rep("white", 13))) %>%
  column_spec(4, background=c(rep("white", 2), 
                              rep("#D3D3D3",2), 
                              rep("white", 12))) %>%
  column_spec(5, background=c(rep("white", 3), 
                              rep("#D3D3D3",2), 
                              rep("white", 11))) %>%
  column_spec(6, background=c(rep("white", 4), 
                              rep("#D3D3D3",2), 
                              rep("white", 10))) %>%
  column_spec(7, background=c(rep("white", 5), 
                              rep("#D3D3D3",2), 
                              rep("white", 9))) %>%
  column_spec(8, background=c(rep("white", 6), 
                              rep("#D3D3D3",2), 
                              rep("white", 8))) %>%
  column_spec(9, background=c(rep("white", 7), 
                              rep("#D3D3D3",2), 
                              rep("white", 7))) %>%
  column_spec(10, background=c(rep("white", 8), 
                               rep("#D3D3D3",2), 
                               rep("white", 6))) %>%
  column_spec(11, background=c(rep("white", 9), 
                               rep("#D3D3D3",2), 
                               rep("white", 5))) %>%
  column_spec(12, background=c(rep("white", 10), 
                               rep("#D3D3D3",2), 
                               rep("white", 4))) %>%
  column_spec(13, background=c(rep("white", 11), 
                               rep("#D3D3D3",2), 
                               rep("white", 3))) %>%
  column_spec(14, background=c(rep("white", 12), 
                               rep("#D3D3D3",2), 
                               rep("white", 2)))
```

@@

```{r check-retention-code}
tapply(acs$below_exp_grade,acs[,c("age","current_grade")], mean)
```

Ok, that looks good. NAs indicate cells with no cases. The 1 values start with 7 year old Kindergarteners and then move down in a perfect diagonal from there. So this looks good.

>>>>

```{r tab-grade-by-age}
acs %>% 
  tabyl(age, current_grade) %>%
  mutate_if(is.numeric, format, big.mark=",") %>%
  kbl(caption="Cross-tabulation of age and current grade of student",
      align=c("l",rep("r",13))) %>%
  kable_paper() %>%
  column_spec(2, background=c(rep("#D3D3D3",2), rep("white", 14))) %>%
  column_spec(3, background=c("white", 
                              rep("#D3D3D3",2), 
                              rep("white", 13))) %>%
  column_spec(4, background=c(rep("white", 2), 
                              rep("#D3D3D3",2), 
                              rep("white", 12))) %>%
  column_spec(5, background=c(rep("white", 3), 
                              rep("#D3D3D3",2), 
                              rep("white", 11))) %>%
  column_spec(6, background=c(rep("white", 4), 
                              rep("#D3D3D3",2), 
                              rep("white", 10))) %>%
  column_spec(7, background=c(rep("white", 5), 
                              rep("#D3D3D3",2), 
                              rep("white", 9))) %>%
  column_spec(8, background=c(rep("white", 6), 
                              rep("#D3D3D3",2), 
                              rep("white", 8))) %>%
  column_spec(9, background=c(rep("white", 7), 
                              rep("#D3D3D3",2), 
                              rep("white", 7))) %>%
  column_spec(10, background=c(rep("white", 8), 
                               rep("#D3D3D3",2), 
                               rep("white", 6))) %>%
  column_spec(11, background=c(rep("white", 9), 
                               rep("#D3D3D3",2), 
                               rep("white", 5))) %>%
  column_spec(12, background=c(rep("white", 10), 
                               rep("#D3D3D3",2), 
                               rep("white", 4))) %>%
  column_spec(13, background=c(rep("white", 11), 
                               rep("#D3D3D3",2), 
                               rep("white", 3))) %>%
  column_spec(14, background=c(rep("white", 12), 
                               rep("#D3D3D3",2), 
                               rep("white", 2)))
```

@@

```{r check-retention-code}
acs %>%
  group_by(age, current_grade) %>%
  summarize(below=mean(below_exp_grade)) %>%
  ggplot(aes(x=current_grade, y=age, fill=below))+
  geom_tile(color="grey20")+
  geom_text(aes(label=below))+
  theme_bw()+
  scale_fill_viridis_c()+
  scale_y_continuous(breaks=5:20, minor_breaks = NULL)+
  labs(x="current grade", y="age", fill="proportion below grade level")
```

Ok, that looks good.
